---
title: "R Markdown Tutorial"
author: "Shahbaz Chaudhary"
date: "11/27/2021"
output: html_document
---

# Yet another reason why you should be familiar with _Markdown_

While Jupyter is the standard tool for Python data scientists, R Studio and R Markdown are the most popular ways R data scientists develop and share their code.

Markdown allows a simple way to format text. For example, you can have _italics_, **bold** and ~~crossed out~~ text.

You can write lists:

- item 1
- item 2
- item 3

You can number your bullets

1. item 1
2. item 2
3. item 3

Or create tables

| column A | Column B | Column C |
| ---     | ---       | ---       |
| value 1| value 2| value 3|
| value 4| value 5| value 6|
| value 7| value 8| value 9|

### But there is more

You can display inline calculations, such as 2 + 2 = `r 2 + 2`!

In fact, you can organize larger chunks of code:

```{r}
seq(10)
```

```{r}
plot(seq(10))
```

You can control what gets displayed in your final document:

```{r echo=FALSE}
plot(seq(10))
```

### Here is a surprise, you can even run Python in RMarkdown (but you need the 'reticulate' library)!

Notice that the following line is not being executed, since there is no '{r}' text.

```
install.packages('reticulate')
```

```{python}
list(range(10))
```

### Better tables
By default, R doesn't do a great job of rendering tables

```{r}
mtcars
```

The tidyverse set of packages promises to do better

```{r}
library(tidyverse)
tibble(mtcars)
```

However, the `knitr` package does a much better job

```{r}
library(knitr)
kable(mtcars)
```
